Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-04-01 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Latex cleanup

A schematic drawing of the instrumentation arrangement is shown in Fig.~\ref{Drawing_Fire_Flamer}.  The thermocouples were mounted on a steel frame.  The frame enabled the thermocouples to be installed at 10~cm intervals from 10~cm to 120~cm above the burner/pan lip/fuel surface. At each 10~cm interval, there were five thermocouples: one centered above the burner/fuel surface and one centered above each edge of the burner/fuel surface, for a total of 70 thermocouples.  A plumb bob and steel tape measure, with a resolution of $\pm$ 0.5~mm, were used to position and align the thermocouples.   The expanded uncertainty for the location of each thermocouple tip is estimated to be $\pm$ 2.5~\%.  The same applies to the location of the heat flux sensor surfaces.

@@

The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW $\pm$ 9~kW with an average total heat release of 23.3~MJ $\pm$ 1.6~MJ over a 300~s period.  The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of 80~kW $\pm$ 24~kW.  The total heat release of the gasoline over the 300~s period after ignition was 13.6~MJ $\pm$ 0.6~MJ.  The polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.  Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of 45~kW $\pm$ 21~kW.  The total heat release over the 300~s period after ignition was 4.1~MJ $\pm$ 0.2~MJ

>>>>

A schematic drawing of the instrumentation arrangement is shown in Fig.~\ref{Drawing_Fire_Flamer}.  The thermocouples were mounted on a steel frame.  The frame enabled the thermocouples to be installed at 10~cm intervals from 10~cm to 120~cm above the burner/pan lip/fuel surface. At each 10~cm interval, there were five thermocouples: one centered above the burner/fuel surface and one centered above each edge of the burner/fuel surface, for a total of 70 thermocouples.  A plumb bob and steel tape measure, with a resolution of $\pm$~0.5~mm, were used to position and align the thermocouples.   The expanded uncertainty for the location of each thermocouple tip is estimated to be $\pm$~2.5~\%.  The same applies to the location of the heat flux sensor surfaces.

@@

The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW~$\pm$~9~kW with an average total heat release of 23.3~MJ~$\pm$~1.6~MJ over a 300~s period.  The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of 80~kW~$\pm$~24~kW.  The total heat release of the gasoline over the 300~s period after ignition was 13.6~MJ~$\pm$~0.6~MJ.  The polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.  Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of 45~kW~$\pm$~21~kW.  The total heat release over the 300~s period after ignition was 4.1~MJ~$\pm$~0.2~MJ
